---
title: "CS 243 Project Graphs"
author: "Caleb Nelson"
date: "December 10, 2017"
output:
  html_document: default
---
##Grid of Graphs - all 48 graphs in one grid for easier comparisons and at-a-glance viewing
### Black line - mean of all 20 trials
### Red line - mean + 1 standard deviation
### Blue line - mean - 1 standard deviation
```{r echo=FALSE}
setwd("C:/Users/User/Documents/GitHub/cs243") #NOTE - please change this to current directory the data is stored in if you want to run this yourself!
data = read.csv("SummarizedData.csv")
data$TimeMinus <- (data$TimeAvg - data$TimeStd)
data$TimePlus <- (data$TimeAvg + data$TimeStd)

par(mar=c(2,2,2,2))
for (y in list ("Time", "OpsTime")){
for (test in list("Sum", "Multiply")){
par(mfrow=c(4, 3))
for (dType in list("int", "float", "long", "char")){
for (platform in list("ASUS Laptop", "Mac", "Raspberry Pi")){
      currentData = data[data$Machine == platform & data$DataType == dType & data$Operation == test, ]
      BufferSize = currentData$Buffer.Size
      if (y == "Time"){
        plot(BufferSize, currentData$TimeAvg, main=paste(platform, dType, test, y), type="l")
        lines(BufferSize, currentData$TimePlus, main=paste(platform, dType, test, y), type="l", col="red")
        lines(BufferSize, currentData$TimeMinus, main=paste(platform, dType, test, y), type="l", col="blue")
      }
      if (y == "OpsTime"){
        plot(BufferSize, currentData$Ops.T.Mean, main=paste(platform, dType, test, y), type="l")
        lines(BufferSize, currentData$Ops.T.Std, main=paste(platform, dType, test, y), type="l", col="red")
        lines(BufferSize, currentData$Ops.T.Dev, main=paste(platform, dType, test, y), type="l", col="blue")
      }
    }
  }
}
}
```

##Individual Graphs - all 48 graphs plotted seperately for better legibility 

```{r echo=FALSE}
for (y in list ("Time", "OpsTime")){
for (test in list("Sum", "Multiply")){
for (dType in list("int", "float", "long", "char")){
for (platform in list("ASUS Laptop", "Mac", "Raspberry Pi")){
      currentData = data[data$Machine == platform & data$DataType == dType & data$Operation == test, ]
      BufferSize = currentData$Buffer.Size
      if (y == "Time"){
        plot(BufferSize, currentData$TimeAvg, main=paste(platform, dType, test, y), type="o")
        lines(BufferSize, currentData$TimePlus, main=paste(platform, dType, test, y), type="o", col="red")
        lines(BufferSize, currentData$TimeMinus, main=paste(platform, dType, test, y), type="o", col="blue")
        legend("topleft", legend=c("Avg+std", "Avg", "Avg-std"), col=c("red", "black", "blue"), pch=15, bty="n")
      }
      if (y == "OpsTime"){
        plot(BufferSize, currentData$Ops.T.Mean, main=paste(platform, dType, test, y), type="o")
        lines(BufferSize, currentData$Ops.T.Std, main=paste(platform, dType, test, y), type="o", col="red")
        lines(BufferSize, currentData$Ops.T.Dev, main=paste(platform, dType, test, y), type="o", col="blue")
        legend("bottomleft", legend=c("Avg+std", "Avg", "Avg-std"), col=c("red", "black", "blue"), pch=15, bty="n")
      }
    }
  }
}
}
```

##Block Data Implementation
###Note: All data measured on the Macbook Pro. The orange line is with a block size of 1, the red line is with a block size of 32, and the blue line is with a block size of 64
####Graph Grid
```{r echo=FALSE}
blockData = read.csv("BlockedPerformanceData.csv")

for (y in list ("Time", "OpsTime")){
par(mfrow=c(2,2))
for (dType in list("int", "float", "long", "char")){
    currentData = blockData[blockData$DataType == dType, ]
    BufferSize = currentData$BufSize
    if (y == "Time"){
      plot(BufferSize, currentData$M01.Time, main=paste(dType, ",", "BufSize vs. Time"), ylab="Time", type="l", col="orange")
      lines(BufferSize, currentData$M32.Time, type="l", col="red")
      lines(BufferSize, currentData$M64.Time, type="l", col="blue")
    }
    if (y == "OpsTime"){
      plot(BufferSize, currentData$M01.Ops.T, main=paste(dType, ",", "BufSize vs. Ops/Time"), ylab="Operations/Time", type="l", col="orange")
      lines(BufferSize, currentData$M32.Ops.T, type="l", col="red")
      lines(BufferSize, currentData$M64.Ops.T, type="l", col="blue")
    }
  }
}
```

####Individual Graphs
```{r echo=FALSE}
for (y in list ("Time", "OpsTime")){
for (dType in list("int", "float", "long", "char")){
    currentData = blockData[blockData$DataType == dType, ]
    BufferSize = currentData$BufSize
    if (y == "Time"){
      plot(BufferSize, currentData$M01.Time, main=paste("Block Implementation for", dType, ",", "BufSize vs. Time"), ylab="Time", type="o", col="orange")
      lines(BufferSize, currentData$M32.Time, type="o", col="red")
      lines(BufferSize, currentData$M64.Time, type="o", col="blue")
      legend("topleft", legend=c("M01", "M32", "M64"), col=c("orange", "red", "blue"), pch=15, bty="n")
    }
    if (y == "OpsTime"){
      plot(BufferSize, currentData$M01.Ops.T, main=paste("Block Implementation for", dType, ",", "BufSize vs. Ops/Time"), ylab="Operations/Time", type="o", col="orange")
      lines(BufferSize, currentData$M32.Ops.T, type="o", col="red")
      lines(BufferSize, currentData$M64.Ops.T, type="o", col="blue")
      legend("bottomleft", legend=c("M01", "M32", "M64"), col=c("orange", "red", "blue"), pch=15, bty="n")
    }
  }
}
```